%-------------------------
% Cover Letter in Latex
% Author : Jim Chen
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Jim Chen} \\ \vspace{1pt}
    \small \href{mailto:jca586@sfu.ca}{\underline{jca586@sfu.ca}} $|$ 
    \href{https://linkedin.com/in/-jimchen-}{\underline{linkedin.com/in/-jimchen-}} $|$
    \href{https://github.com/Jm-Chxn}{\underline{https://github.com/Jm-Chxn}}
\end{center}

\section{}
{\textit{\today}}
\newline
\newline
Crystal Fung
\newline
Software Developer
\newline
WorkSafeBC
\newline
6951 Westminster Hwy
\newline
V7C 1C6
\newline
\newline
\textbf{RE: Software Developer}
\newline
\newline
Dear Crystal Fung,
\newline
\newline
I am writing to express my interest in Software Developer position at WorkSafeBC for the Spring 2025. . As a software engineer passionate about coordinating synergies across the organization to bring opportunities for innovation forward, I am excited about the opporunity to contribute to your team's success. My technical background and problem-solving skills align well with your innovate work in rapid prototyping and development of novel products, services and processes.
\newline
\newline
What particularly draws me to WorkSafeBC is your commitment to make a difference to the workers and employers of B.C.. Throughut my career in technology, I have strived to contribute meaningful solutions to similiar challenges, and I beleive my experience could be valueable to your team. My relevant experiences includes a recent engagement, where I led a cross-functional Scrum team to build Foodie Find, a React-based web application that helps users discover hidden restaurants. I architected the user interface using React.js and Tailwind CSS, integrated real-time data storage with Firebase Realtime Database, and leveraged the Google Maps API to deliver intuitive location services. I led the end-to-end testing strategy—writing over twenty Vitest and React Testing Library suites to validate UI rendering, loading states, and error handling—and managed our CI/CD pipeline on Netlify to guarantee seamless deployments. This project honed my ability to balance rapid feature delivery with rigorous quality assurance and accessibility best practices.
\newline
\newline
Prior to these projects, I served as Student Club Software Engineer for SFU’s Gaming \& Esports Club, where I designed and launched a React/TypeScript site that grew membership to over 3,800 students. As an NFT Analyst at KingDom NFT, I engineered blockchain-driven bots and automated workflows on the Arbitrum-based Magic ecosystem—generating over \$\2250 000 USD in trading volume—and coordinated cross-project partnerships to expand our decentralized offerings. These experiences have refined my abilities in stakeholder collaboration, secure data handling, and delivering user-centric solutions at scale.
\newline
\newline
I truly resonate with the goals and initiatives that WorkSafeBC is fostering. With my solid background in web development and user interface design, I believe I would be a valuable asset to your team. I would greatly appreciate the opportunity to discuss how my skills and experience align with your needs. Thank you for considering my application. I enthusiastically look forward to hearing from you soon.
\newline
\newline
Sincerely,
\newline
\newline
Jim Chen

\end{document}